Enhancing Forecast Reconciliation: A Study of Alternative Covariance Estimators

### 2025-06-17 literature/paper_draft.qmd
Create paper_draft.qmd

---
title: "Draft - Enhancing Forecast Reconciliation: A Study of Covariance Estimation"
author: "Vincent Su"
date: "`r Sys.Date()`"
output: 
  pdf_document
header-includes:
  - \usepackage{bm}
  - \usepackage{titlesec}
  - \titlespacing{\section}{0pt}{30pt plus 12pt minus 1pt}{0pt plus 1pt minus 1pt}
# bibliography: bibliography.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

@@

-   Vector $\bm{y}_t$

-   Matrix $\bm{S}$

-   Covariance matrix of in-sample 1-step-ahead base forecast errors $\hat{\bm{W}}_1$

-   Its shrinkage estimator with diagonal target $\hat{\bm{W}}^{shr}_{1, D}$

-   Its NOVELIST estimator $\hat{\bm{W}}^{shr}_{1, thr}$

@@

# 1. Introduction

@@

@@

# 2. Literature Review

## 2.1 Forecast Reconciliation in Hierarchical and Grouped Time Series

@@

## 2.2 Covariance Estimation in High Dimensions

@@

## 2.3 Relevance to Forecast Reconciliation

@@

# 3. Methodology

## 3.1 Theoretical Framework

@@

Hierarchical/Grouped time series satisfy a set of linear constraints, often represented as: 
$$
\bm{y}_t = \bm{S} \bm{b}_t,
$$ 
where $\bm{S}$ is a summing matrix of order $m x n$ which aggregates the bottom-level series $\bm{b}_t$ ($n$-vector) to the series at aggregation levels above. The $m$-vector $\bm{y}_t$ contains all observations at time $t$

@@

$$
var[y_{t+h} - \tilde{y}_t(h) | F_t] = SPW_hP'S'
$$ where $W_h = E[\hat{e}_t(h) \hat{e}'_t(h) | F_t]$ is the covariance matrix of the h-step-ahead base forecast errors.

@@

## 3.2 Covariance Estimation Approaches

@@

# 4. Simulation

@@

$$
\bm{y}_t = \bm{A} \bm{y}_{t-1} + \bm{e}_t,
$$

where $\bm{A}$ is a $p \times p$ block diagonal matrix of autoregressive coefficients $\bm{A} = diag(\bm{A}_1, \ldots, \bm{A}_m)$, with each $\bm{A}_i$ being a $p_i \times p_i$ matrix. The block diagonal structure ensures that the time series are grouped into $m$ groups, with each group having its own autoregressive coefficients. This aim to simulate the interdependencies between the time series within each group, where reconciliation will be better performed than the usual base forecasts.

The model is added with a Gaussian innovation process $\bm{e}_t$, with covariance matrix $\Sigma$. The covariance matrix $\Sigma$ is generated specifically in the following way:

1. A compound symmetric correlation matrix is used for each block of size $p_i$ in $\bm{A}_i$, where the coefficients are sampled from a uniform distribution.

2. The correlations between different blocks are imposed using the Algorithm 1 in Hardin, Garcia & Golan (2013).

3. The covariance matrix $\Sigma$ is then constructed by uniform sampling of standard deviations for all $p$ series.

We have an option to randomly flip the signs of the covariance elements, which will create a more realistic structure in the innovation process. This is also to simulate the real-world scenario where the observed covariance matrix is not necessarily positive definite.

# 5. Empirical Analysis

@@

# 6. Discussion and Conclusion

>>>>

---
title: "Enhancing Forecast Reconciliation: A Study of Alternative Covariance Estimators"
author: Vincent Su
format: 
  pdf:
    include-in-header:
      text: |
        <!-- \usepackage{amsmath} -->
        <!-- \usepackage{mathspec} -->
        \usepackage{algorithm}
        \usepackage{algpseudocode}
        \usepackage[colorlinks=true, linkcolor=blue, citecolor=blue, urlcolor=blue]{hyperref}
        \usepackage{array}
    mathspec: true
    number-sections: true
execute:
  cache: true
bibliography: D:/Github/Recon_Honours_Thesis/references.bib
# bibliographystyle: apa
csl: D:/Github/Recon_Honours_Thesis/apa.csl
---

@@

-   Vector $\boldsymbol{y}_t$

-   Matrix $\boldsymbol{S}$

-   Covariance matrix of in-sample 1-step-ahead base forecast errors $\hat{\boldsymbol{W}}_1$

-   Its shrinkage estimator with diagonal target $\hat{\boldsymbol{W}}^{shr}_{1, D}$

-   Its NOVELIST estimator $\hat{\boldsymbol{W}}^{shr}_{1, thr}$

@@

# Introduction

@@

## Background

In time series forecasting, aggregation occurs in a variety of settings. A concrete example of a hierarchy would be the Starbucks sales data, where their total sales is the sum of all countries they are operating in, and each national sales is the sum for all cities, and the sales for each city come from many outlets. Data on national tourism, electricity demand, or Gross Domestic Product (GDP) are similar examples of hierarchical time series. The impact of methods for forecasting hierarchical time series has not been limited to academia, with industry also showing a strong interest. Many companies have adopted these methods in practice, including Amazon, the International Monetary Fund, IBM, SAP, and more [@Athanasopoulos2024-as].

The hierarchical structure can be represented as a tree, as shown in @fig-hierarchy. The top level of the tree represents the total value of all series, while the lower levels represent the series at different levels of disaggregation. When there are attributes of interest that are crossed, such as the Starbucks drinks sales at any aggregation level (brand-wise, national, city, or outlet) is also considered by kinds of drinks (e.g., coffees, refreshers), the structure is described as a grouped time series (illustrated in @fig-grouped).

![A 2-level hierarchical tree structure](D:/Github/Recon_Honours_Thesis/research_proposal/figs/hierarchical_structure.png){#fig-hierarchy width="40%"}

![A 2-level grouped structure, which can be considered as the union of two hierarchical trees with common top and bottom level series](D:/Github/Recon_Honours_Thesis/research_proposal/figs/grouped_structure.png){#fig-grouped width="90%"}

For simplicity, we refer to both of these structures as hierarchical time series, we will distinguish between them if and when it is necessary. All hierarchical structures can be represented using matrix algebra:

$$
\boldsymbol{y}_t = \boldsymbol{S} \boldsymbol{b}_t,
$$

where $\boldsymbol{S}$ is a summing matrix of order $n \times n_b$ which aggregates the bottom-level series $\boldsymbol{b}_t \in \mathbb{R}^{n_b}$ to the series at aggregation levels above. The $n$-vector $\boldsymbol{y}_t \in \mathbb{R}^n$ contains all observations at time $t$.

The summing matrix $\boldsymbol{S}$ for the tree structure in @fig-hierarchy is:

$$
\boldsymbol{S} = 
\left[
\begin{array}{cccc}
1 & 1 & 1 & 1 \\
1 & 1 & 0 & 0 \\
0 & 0 & 1 & 1 \\
\multicolumn{4}{c}{\boldsymbol{I_4}}
\end{array}
\right].
$$

@@

# Literature Review

## Forecast Reconciliation in Hierarchical and Grouped Time Series

@@

## Covariance Estimation in High Dimensions

@@

## Relevance to Forecast Reconciliation

@@

# Methodology

## Theoretical Framework

@@

Hierarchical/Grouped time series satisfy a set of linear constraints, often represented as: 
$$
\boldsymbol{y}_t = \boldsymbol{S} \boldsymbol{b}_t,
$$ 
where $\boldsymbol{S}$ is a summing matrix of order $m x n$ which aggregates the bottom-level series $\boldsymbol{b}_t$ ($n$-vector) to the series at aggregation levels above. The $m$-vector $\boldsymbol{y}_t$ contains all observations at time $t$

@@

$$
Var[y_{t+h} - \tilde{y}_t(h) | F_t] = SPW_hP'S'
$$

where $W_h = E[\hat{e}_t(h) \hat{e}'_t(h) | F_t]$ is the covariance matrix of the h-step-ahead base forecast errors.

@@

## Covariance Estimation Approaches

@@

# Simulation

@@

$$
\boldsymbol{b}_t = \boldsymbol{A} \boldsymbol{b}_{t-1} + \boldsymbol{\epsilon}_t,
$$

where $\boldsymbol{A}$ is a $n_b \times n_b$ block diagonal matrix of autoregressive coefficients $\boldsymbol{A} = diag(\boldsymbol{A}_1, \ldots, \boldsymbol{A}_m)$, with each $\boldsymbol{A}_i$ being a $n_{b,i} \times n_{b,i}$ matrix. The block diagonal structure ensures that the time series are grouped into $m$ groups, with each group having its own autoregressive coefficients. This aim to simulate the interdependencies between the time series within each group, where reconciliation will be better performed than the usual base forecasts.

The model is added with a Gaussian innovation process $\boldsymbol{\epsilon}_t$, with covariance matrix $\Sigma$. The covariance matrix $\Sigma$ is generated specifically in the following way:

1. A compound symmetric correlation matrix is used for each block of size $n_{b,i}$ in $\boldsymbol{A}_i$, where the coefficients are sampled from a uniform distribution between 0 and 1.

2. The correlations between different blocks are imposed using the Algorithm 1 in @Hardin2013-wu.

3. The covariance matrix $\Sigma$ is then constructed by uniform sampling of standard deviations, in a range of $[\sqrt{2}, \sqrt{6}]$, for all $n_b$ series.

We have an option to randomly flip the signs of the covariance elements, which will create a more realistic structure in the innovation process. This can be done by pre- and post-multiplying $\Sigma$ by a random diagonal matrix $\boldsymbol{V}$ with entries sampled from $\{-1, 1\}$, yielding $\Sigma^* = \boldsymbol{V} \Sigma \boldsymbol{V}$.

For each series, $T = 116$ or $316$ observations are generated. The first 100 or 300 observations are used for training, and the last 16 observations are used for testing. The remaining data is used to compute the best fitted ARIMA models by minimising the AICc criterion, in which we use the automatic algorithm from Fabletools R package [@fabletools-fa]. We refer to them as base models, and their base forecasts are then reconciled using the MinT with different covariance estimators. These include using the unbiased sample covariance matrix - MinT(Sample), the shrinkage estimator - MinT(Shrink), and the NOVELIST estimator - MinT(N). The Monte Carlo simulation is repeated $M = 10000$ times, in which the parameters for data generating process is fixed.

# Empirical Analysis

@@

# Discussion and Conclusion
